Properties of coronal Fourier power spectra and their implications for coronal seismology and coronal heating.

### 2014-04-29 tex/paper1/paper1.tex
paper edits

This has been recognized by \cite{2010MNRAS.402..307V} in the study of
XMM-Newton observations of highly variable Seyfert 1 galaxies.
\cite{2010MNRAS.402..307V} presents a model comparison and fitting
technique that can be used to determine the presence of a narrow-band
features in Fourier power spectra against a red-noise like background
emission.  This technique is applicable to the search for oscillatory
power in coronal time-series.

>>>>

Even this approach to identifying oscillatory power is not quite
complete, as it simply rejects the null hypothesis that the power
spectrum can be adequately explained by a red-noise power spectrum.
Model comparison similar to that described in Section \ref{sec:anal}
is required to prefer a model with oscillatory content over one
without. The difficulty in finding narrow-band features in Fourier
power spectra against a red-noise background power spectrum has been
recognized by \cite{2010MNRAS.402..307V} in the study of XMM-Newton
observations of highly variable Seyfert 1 galaxies.
\cite{2010MNRAS.402..307V} presents a model comparison and fitting
technique is directly applicable to the search for oscillatory power
in coronal time-series.
